\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2010-11-23 doc/USER_MANUAL/manual_SPECFEM3D.tex
added a sentence about the path to the SCOTCH source code
moves unused/old/deprecated files and routines into SPECFEM3D/utils/unused_routines; updates manual and Makefiles

The SCOTCH library \citep{PeRo96}
provides efficent static mapping, graph and mesh partitioning routines. SCOTCH is a free software package developed by
Fran\c {c}ois Pellegrini et al. from LaBRI and INRIA in Bordeaux, France, downloadable from the web page \url{https://gforge.inria.fr/projects/scotch/}. It is more recent than METIS, actively maintained and performs better in many cases.
The path to the SCOTCH installation needs to be set with the option \texttt{-{}-with-scotch-path}. Just as an example:
\begin{lyxcode}
./configure~FC=ifort~MPIFC=mpif90~-{}-with-scotch-path=/opt/scotch
\end{lyxcode}

@@

An efficient partitioning is important because it leverages the overall running time of the application.
It amounts to balance the number of elements in each slice while minimizing the communication costs
resulting from the placement of adjacent elements on different processors. \texttt{decompose\_mesh\_SCOTCH} depends on the SCOTCH library \citep{PeRo96},
which provides efficent static mapping, graph and mesh partitioning routines. SCOTCH is a free software package developed by
Fran\c {c}ois Pellegrini et al. from LaBRI and INRIA in Bordeaux, France, downloadable from the web page \url{https://gforge.inria.fr/projects/scotch/}. It is more recent than METIS, actively maintained and performs better in many cases.
\\

@@

\subsection{\texttt{movie2gif.pl}}

With the movie data saved in \texttt{in\_out\_files/OUTPUT\_FILES/} at the end of
a movie simulation (\texttt{\small MOVIE\_SURFACE=.true.}), you can
run the \texttt{`create\_movie\_GMT}' code to convert these binary
movie data into GMT xyz files for futher processing. A sample script
\texttt{movie2gif.pl} is provided to do this conversion, and then
plot the movie snapshots in GMT, for example:

\begin{lyxcode}
movie2gif.pl~-m~CMTSOLUTION~-g~-f~1/40~-n~-2~-p~
\end{lyxcode}
which for the first through the 40th movie frame, converts the \texttt{moviedata}
files into GMT xyz files, interpolates them using the 'nearneighbor'
command in GMT, and plots them on a 2D topography map. Note that `\texttt{-2}'
and `\texttt{-p}' are both optional.

\subsection{\texttt{plot\_shakemap.gmt.pl}}

>>>>

The SCOTCH library \citep{PeRo96}
provides efficent static mapping, graph and mesh partitioning routines. SCOTCH is a free software package developed by
Fran\c {c}ois Pellegrini et al. from LaBRI and INRIA in Bordeaux, France, downloadable from the web page \url{https://gforge.inria.fr/projects/scotch/}. It is more recent than METIS, actively maintained and performs better in many cases.
A recent version of its source code is provided in directory \texttt{src/decompose\_mesh\_SCOTCH/scotch\_5.1.10b}.
The path to the SCOTCH installation needs to be set with the option \texttt{-{}-with-scotch-path}. Just as an example:
\begin{lyxcode}
./configure~FC=ifort~MPIFC=mpif90~-{}-with-scotch-path=/opt/scotch
\end{lyxcode}

@@

An efficient partitioning is important because it leverages the overall running time of the application.
It amounts to balance the number of elements in each slice while minimizing the communication costs
resulting from the placement of adjacent elements on different processors. \texttt{decompose\_mesh\_SCOTCH} depends on the SCOTCH library \citep{PeRo96},
which provides efficent static mapping, graph and mesh partitioning routines. SCOTCH is a free software package developed by
Fran\c {c}ois Pellegrini et al. from LaBRI and INRIA in Bordeaux, France, downloadable from the web page \url{https://gforge.inria.fr/projects/scotch/}. It is more recent than METIS, actively maintained and performs better in many cases.
A recent version of its source code is provided in directory \texttt{src/decompose\_mesh\_SCOTCH/scotch\_5.1.10b}.
\\

@@

\subsection{Script \texttt{movie2gif.gmt.pl}}

With the movie data saved in \texttt{in\_out\_files/OUTPUT\_FILES/} at the end of
a movie simulation (\texttt{\small MOVIE\_SURFACE=.true.}), you can
run the \texttt{`create\_movie\_shakemap\_AVS\_DX\_GMT}' code to convert these binary
movie data into GMT xyz files for futher processing. A sample script
\texttt{movie2gif.gmt.pl} is provided to do this conversion, and then
plot the movie snapshots in GMT, for example:

\begin{lyxcode}
movie2gif.gmt.pl~-m~CMTSOLUTION~-g~-f~1/40~-n~-2~-p~
\end{lyxcode}
which for the first through the 40th movie frame, converts the \texttt{moviedata}
files into GMT xyz files, interpolates them using the 'nearneighbor'
command in GMT, and plots them on a 2D topography map. Note that `\texttt{-2}'
and `\texttt{-p}' are both optional.

\subsection{Script \texttt{plot\_shakemap.gmt.pl}}
